

\documentclass[A4,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{xcolor} 

\usepackage{fontawesome5}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\renewcommand\labelenumi{[\theenumi]}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\ 
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \text{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
\textbf{\Huge \scshape Chandan Prakash} \\ \vspace{1pt}
\small 
{\href{mailto:sanchittanwar75@gmail.com}{{\textbf{\underline{abchandan11@gmail.com}}}}} $|$  
{\href{https://github.com/b18050}{{\textbf{\underline{github.com/b18050}}}}} $|$ 
{{\textbf{+19432395727}}} $|$ 
{\href{https://www.linkedin.com/in/abchandan11/}{{\textbf{\underline{linkedin.com/in/abchandan11}}}}} 
$|$ {\href{https://sites.gatech.edu/abchandan11/}{{\textbf{\underline{\textcolor{blue}{website}}}}}} 
$|$ {\textbf{Atlanta, GA}}
\end{center}


%% Summary section: https://chatgpt.com/share/67140fec-d88c-8000-8be0-3e0656d584dc

\vspace{-4.5mm}
%-----------EDUCATION-----------
\section{\textcolor{NavyBlue}{Education}}
  \begin{itemize}[leftmargin=0in, label={}]
    \item \textbf{Georgia Institute of Technology} \hfill  \textit{Atlanta, GA } \\
    \textit{Master of Science in Computer Science (GPA : 4.0)  \hfill \textit{Dec. 2025}}
    
    % \vspace{-1mm}  % Adjusts spacing
    % \begin{itemize}[leftmargin=0.25in, label={}]
    %     \small{
    %         \item \textbf{Relevant Courses:} Deep Learning, Vision Language Models, Machine Learning, Reinforcement Learning, Computer Vision, LLM
    %     }
    % \end{itemize}

   % Reduces space between sections

    \item \textbf{Indian Institute of Technology (IIT) } \hfill \textit{ Mandi, India} \\
    \textit{Bachelor of Technology in Computer Science} \hfill \textit{ May 2022}
  \end{itemize}

 \vspace{-4.5mm}
 
\section{\textcolor{NavyBlue}{Skills}}
 \begin{itemize}[leftmargin=0in, label={}]
    \normalsize{
    \item{
    \textbf{Programming and Frameworks:}  Python, Java, C++, JavaScript/TypeScript, React, Next.js, Node.js (Express), Dropwizard }
     \vspace{-1.5mm}
    \item {\textbf{Cloud and Infrastructure:} AWS, Docker, Kubernetes, Terraform, Git, CI/CD pipelines, System design
    } 
     \vspace{-1.5mm}
    \item {\textbf{Data and Visualization:} MySQL, Postgres, MongoDB; Highcharts, D3.js; REST/GraphQL APIs; JUnit, PyTest}
}
 \end{itemize}

 \vspace{-4.5mm}
%-----------EXPERIENCE-----------

\section{\textcolor{NavyBlue}{Work Experience}}
  \begin{itemize}[leftmargin=0in, label={}]
     \item \textbf{\fontsize{11}{12}\selectfont 
     Goldman Sachs - Software Engineering Intern} \hfill  Dallas, TX \textbar \textit{Jun. 2025 - Aug. 2025} \\
    \vspace{-1mm}
    \begin{itemize}[leftmargin=0.25in, label=$\bullet$]  % Use star bullets for the rest of the items
            \item{Designed and deployed an event-driven, compliance-validated tax-harvesting engine for Private Wealth Management, integrating Kafka to process 500+ models simultaneously and reduce client tax liabilities by X\%.}
            \item{Developed a full-stack tax configuration platform (Java, MongoDB, React) with modular APIs, feature switches; adopted by team of 100+ traders, advisors and cutting peak-season manual processing by 100\%.} 
    \end{itemize}

    \vspace{-2mm}

 \item \textbf{\fontsize{11}{12}\selectfont Lead Software Developer - Internet Intelligence Lab, Georgia Tech} \hfill Atlanta, GA \textbar \textit{Aug. 2024 - May 2025} \\
    \textit{Advisors: \textit{Prof. Amanda Meng, Prof. Alberto Dainotti}}
    \vspace{-2mm}
    \begin{itemize}[leftmargin=0.25in, label=$\bullet$]  % Use star bullets for the rest of the items
        {
            \item{Refactored 50+ class-based components to function-based components with Redux state management, supporting modern CSS libraries and improving UI maintainability and responsiveness. } 
            \item Integrated 2 new network outage signals and Notion-based configuration updates into interactive dashboards using Highcharts and D3.js, delivering real-time visualizations that localized connectivity signals [\href{https://ioda.inetintel.cc.gatech.edu/reports/ioda-further-localizes-connectivity-signals/}{\textcolor{blue}{\textbf{\underline{Report}}}}] 
        }
    \end{itemize}
    \vspace{-2mm}


 \item \textbf{\fontsize{11}{12}\selectfont Oracle Corporation - Software Engineer} \hfill \textit{Bengaluru, India \textbar\  Jun. 2022 -- Jul. 2024} \\
    \vspace{-1mm}
  \begin{itemize}[leftmargin=0.25in, label=$\bullet$]
  \item{Contributed code heavily to an SOP automation platform from concept to feature end to end; written REST APIs, data models, developed UIs; reducing Ops troubleshooting production issues time from weeks to hours.}
    \item{Built an automated log monitoring service that reduced manual troubleshooting adopted by team of 30+ engineering.}
    \item{Built an in-memory wrapper for workflow-as-a-service, enabling developers to test cloud-based workflows locally without deploying to the cloud and without affecting actual clusters enabling faster SOP development.}
    \item {Developed and managed 20+ RESTful APIs (Dropwizard, J2EE) powering multi-cloud services, with 80\% unit test coverage; processed 5K+ daily requests with low-latency response times.}
    \item{Migrated frontend from Java FTL to React within a microservice architecture, boosting load speed by 40\%.}
  \end{itemize}
    \vspace{-2mm}

    \item \textbf{\fontsize{11}{12}\selectfont Google Summer of Code - Open Source} \hfill \textit{Remote, India \textbar\  May. 2021 -- Aug. 2021} \\
    \vspace{-1mm}
  \begin{itemize}[leftmargin=0.25in, label=$\bullet$]
    \item{Developed a TypeScript React wrapper for p5.js, adding type support and compatibility for our use case, improving rendering performance by 25\% in visualization-heavy applications.} [\href{https://github.com/b18050/gsoc-musicblocks-graphics-management}{\textcolor{blue}{\textbf{\underline{Report}}}}] 
  \end{itemize}
\vspace{-2mm}

    

    
  \end{itemize}
\vspace{-4.5mm}






%-----------PROJECTS-----------
\section{\textcolor{NavyBlue}{Projects}}

\begin{itemize}[leftmargin=0in, label={}]

    %--- Project 1 ---
    \item  \textbf{\href{https://github.com/b18050/visara}{\faIcon{link} VISARA - Agentic LLM }} 
 \hfill \textit{Jan. 2023 -- Jul. 2024}
  \vspace{-1.5mm}
    \begin{itemize}[leftmargin=0.25in]
        \item Built an AI software which generates reports for internet outages leveraging Llama offline for potential 500+ users.
        \item Engineered feature for user to review and edit reports, combining real-time outage data with contextual news, effectively functioning as a ChatGPT-style assistant for outage reporting.
    \end{itemize}
     \vspace{-1.5mm}
    %--- Project 2 ---
    % \item \textbf{\href{https://github.com/b18050/visara}{\faIcon{link} equibid.io}} \hfill \textit{Aug. 2024 -- Sep. 2025}
    %  \vspace{-1.5mm}
    % \begin{itemize}[leftmargin=0.25in]
    %     \item Built an ML-powered full-stack horse auction platform aggregating lots from 10+ global websites, with a web-based admin dashboard managing 10+ concurrent auctions.
    %     \item Developed modular Python scrapers and data pipelines to process 2+ TB of multimedia, upload to S3, and integrate deep learning models for real-time predictions.
    % \end{itemize}

    \item \textbf{\href{https://github.com/b18050/visara}{\faIcon{link} equibid.io}} \hfill \textit{Aug. 2024 -- Sep. 2025}
 \vspace{-1.5mm}
\begin{itemize}[leftmargin=0.25in]
    \item Built full-stack horse auction platform aggregating data from 10+ international auction houses using Flask, PostgreSQL, and Wasabi S3, 
    automating data collection with Python web scrapers that reduced manual processing by 90\%.
    \item Engineered 10+ modular scrapers (Selenium, BeautifulSoup) processing 2+ TB multimedia data with automated retry mechanisms, 
    concurrent downloads, and 3-hour sync schedules achieving 99.9\% uptime.
    \item Implemented enterprise authentication (TOTP/SMS 2FA via Twilio) with role-based access control and responsive admin dashboard managing
     real-time auction monitoring, video processing pipelines, and ML-enriched catalog visualization for 50+ users.
\end{itemize}
    % %--- Project 3 ---
    %  \vspace{-1.5mm}
    % \item \textbf{\href{https://github.com/b18050/buzzdb-graph}{\faIcon{link} BuzzDB - C++}} \hfill \textit{Aug. 2024 -- Dec. 2024}
    %  \vspace{-1.5mm}
    % \begin{itemize}[leftmargin=0.25in]
    %     \item Implemented thread-safe graph-based indexing in C++ to replace B+ trees in BuzzDB, boosting complex social media query performance by 30\% and earning top 3 recognition among 200 students.
    % \end{itemize}



\end{itemize}

%-------------------------------------------

% resume_helper keywords start
% generated 2025-10-04 06:42 UTC
\par
{\color{white} incidents oci developing solutions innovative technologies operational excellence cloud-scale incidents efficiency preventing engineering dedicated excellence measurably large-scale incidents world-class solutions automation solutions building world-class cloud infrastructure designing developing developing resilient hands-on engineering managing large-scale developing advanced duration recurrence effectively analyze prevent cloud-scale preventing managing services automation}
% resume_helper keywords end

\end{document}
